\huge Tor's Usability for Censorship Circumvention

### 2016-04-17 pets2017-paper/pets2017-paper.tex
deleting comments
update numbers to correct for overestimating time on progress bar
count bridge choices from attempts.csv
calculate median times with DNFs

%TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.
\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 4:01 \\
	E3-NEW & 13/20 & 65\% & 12:38 \\
	E3-OLD & 10/20 & 50\% & 18:16 \\
	\end{tabular}
\caption{{\color{red} TODO: FIX THIS SO THAT MEDIAN TIMES REFLECT DNF=40 minutes.}
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were not used to calculate the median time
to success.}
\label{table:participant-summary}
\end{table}

@@

\begin{figure} 
%\includegraphics{}
{\color {red} TODO} 
\caption{order pluggable transports were chosen}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
{\color{red} MAKE THIS FOR ACTIVE TIME}
}
\label{fig:active_time_clamped}
\end{figure}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 23\% & 52\% & 23\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 17\% & 58\% & 25\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 27\% & 40\% & 29\% & 3\% \\
	E3 & 20\% & 57\% & 21\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

@@

>>>>

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:05 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 5:07 \\
	E3-NEW & 13/20 & 65\% & 22:19 \\
	E3-OLD & 10/20 & 50\% & 40:08 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned success time for 40 minutes.}
\label{table:participant-summary}
\end{table}

@@

@@

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 22\% & 57\% & 19\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 18\% & 63\% & 19\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 29\% & 48\% & 20\% & 2\% \\
	E3 & 19\% & 61\% & 18\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

@@

% impacts of giving people advice on which transport to choose.
10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
5 people in the old interface chose meek as their second bridge (5/13, 38\%).
